### 2018-09-14 manuscript.tex
Update manuscript.tex

Multiple theoretical frameworks would have to be incorporated to grasp a full explanation of the persistence and decline of FGC due to the heterogeneity of the population \cite{Hayf05, EffeVogt15, ModrLiu13}.  Identifying benefits of FGC practice is crucial to promote sustainable change \cite{EffeVogt15}, and a community-based FGC perspective \cite{BoylCorl010, Drol11,Hayf05, Grue05, Hodg11, KandNwak09, OdukAfol17} (to confirm) should also be recognized.  This study takes both the dynamics of attitudes and intention of FGC practices (beliefs of FGC benefits, and intention of cutting) into account at both a population and a community level to test whether FGC is a result of social interactions of social agents through interpreting norms in expectance of rewards. \jd{This P. seems insufficient to tie the theoretical explanation to our research questions. We should study Efferson's approach.} \cf{good point. reframed and may still need more thoughts.}

\subsection{Research Questions}\label{research-questions}
The main focus of this study is to analyze associations of attitudes of FGC benefits (see the list of FGC benefits at table xx) and intention (planned behavior) to cut daughters.  Additionaly, we also study the association of attitudes of FGC benefits and of FGC continuance; and the association of attitudes of FGC benefits, FGC continuance and intention (planned behavior) of cutting daughters (structural models) (to explain why) 
\jd{I can work on the structural part, but we need a clear explanation of what we are trying to learn from the main question.}
\jd{I guess this is also a good place to discuss our community variables?}

>>>>

Multiple theoretical frameworks would have to be incorporated to grasp a full explanation of the persistence and decline of FGC due to the heterogeneity of the population \cite{Hayf05, EffeVogt15, ModrLiu13}.  Identifying benefits of FGC practice is crucial to promote sustainable change \cite{EffeVogt15}, and a community-based FGC perspective \cite{BoylCorl010, Drol11,Hayf05, Grue05, Hodg11, KandNwak09, OdukAfol17} (to confirm) should also be recognized.  This study takes both the dynamics of attitudes and intention of FGC practices (beliefs of FGC benefits, and intention of cutting) into account at both a population and a community level to test whether FGC is a result of social interactions of social agents through interpreting norms in expectance of rewards. \jd{This P. seems insufficient to tie the theoretical explanation to our research questions. We should study Efferson's approach.} \cf{good point. reframed and may still need more works.}

\subsection{Research Questions}\label{research-questions}
The main focus of this study is to analyze associations of attitudes towards FGC benefits (see the list of FGC benefits at table xx) and intention to cut daughters in the hope that if patterns of social norms associating behavioral intenation can be detected at both a population and a community level.  If so, if social norms the most soundly

Additionaly, we also study the association of attitudes of FGC benefits and of FGC continuance; and the association of attitudes of FGC benefits, FGC continuance and intention (planned behavior) of cutting daughters (structural models) (to explain why) 
\jd{I can work on the structural part, but we need a clear explanation of what we are trying to learn from the main question.} \cf{reframed the main question.}
\jd{I guess this is also a good place to discuss our community variables?}
